Recently, a new concept of multistream is introduced. Under this problem setting, 
two data streams are involved, which are referred as source and target streams. The 
source stream continuously generates data instances from a certain domain with 
labels, while the target stream continuously generates data instances from another 
domain without labels. Existing approaches assume that domains for both data streams 
are identical, which is not quite true in reality, since data streams from different 
sources may contain distinct features, more specifically, different number of features. Furthermore, obtaining labels for every instance 
in data streams is often expensive and time-consuming. Therefore, whether labeled 
instances from related streams can be helpful to predict the unlabeled instances in 
a certain stream becomes an important topic to explore. In this paper, domains between 
source and target streams may have distinct feature spaces and data distributions. 
Our objective is to predict class labels of data instances in the target stream by 
using the classifiers trained in the source stream.

We propose a semi-supervised framework of multistream classification by using projected data from a common latent domain, which is projected from both source and target domains. At the same time, empirical valuation and analysis 
on both synthetic and real-world datasets are performed to validate the effectiveness 
of our proposed algorithm, comparing to state-of-the-art techniques. Experiment results 
show that our approach significantly outperforms other existing benchmarks.